\myTitle

### 2024-02-03 body-text-of-paper.tex
started writing the discussion- hey! 3 paragraphs!

We refer to the structure used to implement this cross-validation simulation
of admixed individuals as
a {\em genomic simulation pedigree} or GSP.  Like any pedigree,
a GSP includes a set of founders (individuals that have no parents specified in the
pedigree), and it includes non-founders; however, we introduce an additional node
type in the GSP that represents samples taken from the non-founders. These samples
are the simulated admixed individuals.  A GSP must have no inbreeding loops, since
any inbreeding loop indicates that more than one copy of a gene in an ancestor may
be created amongst its descendants, which is a type of sampling without
replacement.  Furthermore, in a GSP, the amount of genetic material taken from the
samples at the sample nodes should be equal to the amount of material in the founders,
to ensure that all available data is being used to estimate power for the estimation of
admixture fractions.

@@

Somewhere here I want to mention that the Anderson et al. (2008) approach for simulating
mixtures of genotypes to assess how well one can estimate mixture proportions---the fraction
of individuals from each of a set of baseline or reference populations---allows the user to
simulate, if desired, more genotypes than occur in the reference samples.  This is because
a trick is done in the inference stage to remove the correlation between the simulated individual
and the reference sample, relative to the true population, by removing the simulated individual's
genotypes from its own reference population when calculating the likelihood that its genotype
originated from each of the reference populations.  To do the same when doing simulations for
assessing power using ADMIXTURE or STRUCTURE would require hacking the underlying code
of those programs, which is not desirable.  So, for these cases we have used the sampling
without replacement approach.

>>>>

We refer to the structure used to implement this cross-validation simulation
of admixed individuals as
a {\em genomic simulation pedigree} or GSP.  Like any pedigree,
a GSP includes a set of founders (individuals that have no parents specified in the
pedigree), and it includes non-founders; however, we introduce an additional node
type in the GSP that represents samples taken from the non-founders. These samples
are the simulated admixed individuals.  A GSP must have no inbreeding loops, since
any inbreeding loop indicates that more than one copy of a gene in an ancestor may
be created amongst its descendants, which is a type of sampling with
replacement.  Furthermore, in a GSP, the amount of genetic material taken from the
samples at the sample nodes should be equal to the amount of material in the founders,
to ensure that all available data is being used to estimate power for the estimation of
admixture fractions.

@@

Here, we present \gscramble{}, a simulation approach for creating biologically informed individual 
genotypes of different hybrid classes. Two integral features of \gscramble{} are: 
1) alleles are sampled from populations without replacement and 
2) alleles are segregated based on species-specific recombination rates. 
Our results show that both 
of these features are especially important for accurately reflecting empirical data from large genetic 
marker sets (thousands of markers), 
which are common from next generation sequencing methods. Sampling alleles without 
replacement, and thereby preserving the genetic differences (or lack thereof) of populations is 
essential for avoiding the issue of RISPI---an issue that is exacerbated as the number of 
alleles sampled for an individual increases. Additionally, we show the importance of accounting for 
the physical linkage of markers when large marker sets are used and that treating loci as 
independent results in erroneously reduced variation in the estimation of individuals' admixture 
fractions.

\gscramble{} is conducive for numerous types of contemporary marker data sets. As mentioned above, 
one key feature of \gscramble{} is the integration of recombination rates, thereby accounting for physical 
linkage which is expected among larger contemporary data sets. Furthermore, \gscramble{} performs marker 
segregation with computational efficiency---for the four different GSPs used with the invasive wild pig data set, 
the mean run time of each simulation with 14,233 SNP loci was 2.3 seconds (range: 1.9-5.7 $s$). 
While \gscramble{} is equally applicable to data sets with 
microhaplotypes \citep{baetscher2018microhaplotypes} or microsatellites \citep{zhan2017megasat}, 
it is not suited for genotype likelihood data (i.e. from low-coverage whole genome sequencing). 
The \gscramble{} simulation approach involves the segregation of gametes and therefore requires 
that genotypes are resolved.

We envision \gscramble{} to be relevant for a diverse range of potential applications. In our 
provided empirical examples with trout and wild pig data, we demonstrate the basics of 
creating hybrid classes. Similarly, \gscramble{} has recently been used to demonstrate the 
power for hybrid classification of a population genetics method used to differentiate wild pigs with 
wildboar introgression from domestic pigs \citep{smyser2024probgen}. In \citet{smyser2024probgen}, 
researchers made use of the segregation options in \gscramble{} in order to preserve founder individuals' 
genotypes within populations (in contrast to \textit{a priori} shuffling alleles within populations) in order to 
retain the subpopulation structure present within certain populations---thereby, better reflecting the 
actual admixture variation expected from wildboar and domestic pig hybrids. We think \gscramble{} 
may also be useful for assessing relatedness estimates using pedigrees of varying complexity. Here, it 
is important to note that each time a gamete is segregated in a GSP, its complement is also 
segregated---an example of antithetical variate sampling in Monte Carlo methods. Thus, in the 
example of relatedness, fixed specified founders should be repeatedly "mated" with one offspring 
sampled per iteration to avoid sampling of anticorrelated genotypes.

\textbf{Eric's notes}: 
Somewhere here I want to mention that the Anderson et al. (2008) approach for simulating
mixtures of genotypes to assess how well one can estimate mixture proportions---the fraction
of individuals from each of a set of baseline or reference populations---allows the user to
simulate, if desired, more genotypes than occur in the reference samples.  This is because
a trick is done in the inference stage to remove the correlation between the simulated individual
and the reference sample, relative to the true population, by removing the simulated individual's
genotypes from its own reference population when calculating the likelihood that its genotype
originated from each of the reference populations.  To do the same when doing simulations for
assessing power using ADMIXTURE or STRUCTURE would require hacking the underlying code
of those programs, which is not desirable.  So, for these cases we have used the sampling
without replacement approach.
